Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-06 aistats/paper.tex
Write about kakade paper

\clearpage
\section{Plan}

\begin{enumerate}
	\item intro to exponential family, and density estimation
	\item the thing we want to bound
	\item Examples : gaussian mean and gaussian variance (+other examples, just mentioned)
	\item Insight : Strongly convex case. (+ self-concordance that is not verified either)
	\item insight : bias-variance decomposition
	\item Optimization perspective : SBPP or SBG. But no analysis hold, revealing a flaw of all these techniques.
	\item Discussion : we believe finding a convergence rate would bring new tools useful to deal with common objects such as barrier losses.
\end{enumerate}

Open questions
\begin{itemize}
	\item does a base measure change anything ?
	\item is there multiple conjugate priors ?
	\item misspecified case. Do we have a   formula ?
\end{itemize}

>>>>

\section{Group Meeting}
\begin{enumerate}
	\item new plots : mirror map, and gaussian trajectories
	\item the MLE is biased according to our definition. See plots. Does this definition of bias make sense ? An unbiased estimator's primal mean would be equal to the optimum, vs the dual mean. 
	\item \citet{kakade2010learning}
	\begin{enumerate}
		\item assumption in the spirit of infinite order self-concordance only at the optimum
		\item After a burn-in phase, the loss behaves quadratically. No precise description of the burn-in length.
		\item conclusion : it is worth writing down until the end what we are obtaining with self-concordance. \RLP{TODO}
		\item idea 1 : try to express some of their results with the mean parameter instead.
		\item idea 2 : using their assumption on the mirror map, perform a Newton kind of analysis for SMD. (exploiting the link MAP -> optimization).
	\end{enumerate}
\end{enumerate}

\section{Plan}
\begin{enumerate}
	\item intro to exponential family, and density estimation
	\item the thing we want to bound
	\item Examples : gaussian mean and gaussian variance (+other examples, just mentioned)
	\item Insight : Strongly convex case. (+ self-concordance that is not verified either)
	\item insight : bias-variance decomposition
	\item Optimization perspective : SBPP or SBG. But no analysis hold, revealing a flaw of all these techniques.
	\item Discussion : we believe finding a convergence rate would bring new tools useful to deal with common objects such as barrier losses.
\end{enumerate}

Open questions
\begin{itemize}
	\item does a base measure change anything ?
	\item is there multiple conjugate priors ?
	\item misspecified case. Do we have a   formula ? Partial answer : a sufficient condition is to have $\mu^*$ be accessible to our model, even if the true distribution is not.
\end{itemize}
